\papertitle

### 2012-10-13 manuscript.tex
Fixed dash mistakes.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\begin{figure}[!tb]
\centering
\includegraphics[width=\linewidth]{figures/h2bird.png}
\caption{H$^2$Bird ornithopter MAV}
\label{fig:h2bird}
\end{figure}
The power, size, and weight constraints of micro air vehicle (MAV) 
platforms significantly limit on-board sensing and computational 
resources, and thus the complexity of the control and state estimation 
algorithms which can be executed on-board. These constraints are 
particularly severe for flapping wing MAVs, a class of MAVs that have inherently superior 
safety, and noise profile to rotor craft MAVs, but at the 
expense of payload weight.
%Intro portion about previous works in ornithopter coorperative control/
%modeling ( won't necessarily stay in this spot)
Modeling and control of flapping wing MAVs is becoming a well studied subject\cite{floreano:flying}. 
Shigeoka discusses velocity and altitude control in ~\cite{Shigeoka:ornithopter}. 
Design and control of the sub--15 gram DelFly ornithopter is described by 
deCroon et al.~\cite{delfly:design}. In contrast, there is little previous work 
on guidance of flapping wing MAVs. Baek demonstrated altitude control with an external 
camera~\cite{baek:altitude}. de Croon et al. demonstrated obstacle avoidance 
with an onboard camera and offboard processing~\cite{delfly:avoid}. For sub--20 gram
ornithopters, Baek et al. \cite{baek:tracking} is one of the few examples of
completely autonomous target seeking.
%[However, these papers do not study the system blah blah blah.]

@@

Rather than power-intensive PC processors, we used the ARM-based 
BeagleBoard single-board computer as reference computation platform. The
BeagleBoard consumes approximately 1 watt while running our computer vision 
and control algorithms. It uses the same processor as popular sub--10 gram 
processor modules--such as the Gumstix Overo and LogicPD Torpedo--which are 
light enough for deployment on millirobotic ground vehicles. We pair the 
BeagleBoard with an off-the-shelf consumer USB web camera, for similar image 
quality and resolution to the miniature camera modules available at 
millirobot scale. The BeagleBoard communicates with the H$^2$Bird using a 
USB radio module which implements the IEEE 802.15.4 wireless standard.
%TODO footnotes: Gumstix, LogidPD

@@

Attitude estimation and control for the H$^2$Bird runs on-board to achieve 
maintain high-sample-rate attitude control. We estimate the vehicle pose by naively
integrating the IMU, and use a proportional plus integral plus derivative (PID) 
controller for controlling the vehicle.

@@

The results of our experimental trials are shown in
Figs.~\ref{fig:flight_paths} and~\ref{fig:flight_paths_feasible}. For
initial conditions in the middle of the testing space and in front of the
camera, we achieved a success rate of 80\%. This case is depicted in
Fig.~\ref{fig:flight_paths_feasible}. As we moved towards the edges of the
feasible region in Fig.~\ref{fig:flight_paths}, the success rate diminishes
to 50\% because of several factors. On the edges of the camera frame, the yaw
control inputs are large in magnitude, although this is not necessary in all
cases. Since the control algorithm we are using has no notion of depth, it
applies the same control input whether the ornithopter is close to the camera,
where small changes in heading are adequate, or far away from the camera,
where large changes in heading are necessary. Due to this phenomenon, the
controller often over or under--compensates in certain regions, depending upon
the PID tuning and the distance from the camera. Tracking noise can also cause
passage negotiation to fail. Variations in the H$^2$Bird hand launch can cause
the system to respond differently for similar initial conditions. In addition,
the H$^2$Bird battery was changed approximately every 5 tests, adding more
variation to the H$^2$Bird performance by affecting the motor power output.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\begin{figure}[!tb]
\centering
\includegraphics[width=\linewidth]{figures/h2bird.png}
\caption{H$^2$Bird ornithopter MAV}
\label{fig:h2bird}
\end{figure}
The power, size, and weight constraints of micro air vehicle (MAV) 
platforms significantly limit on-board sensing and computational 
resources, and thus the complexity of the control and state estimation 
algorithms which can be executed on-board. These constraints are 
particularly severe for flapping wing MAVs, a class of MAVs that have inherently superior 
safety, and noise profile to rotor craft MAVs, but at the 
expense of payload weight.
%Intro portion about previous works in ornithopter coorperative control/
%modeling ( won't necessarily stay in this spot)
Modeling and control of flapping wing MAVs is becoming a well studied subject\cite{floreano:flying}. 
Shigeoka discusses velocity and altitude control in ~\cite{Shigeoka:ornithopter}. 
Design and control of the sub-15 gram DelFly ornithopter is described by 
deCroon et al.~\cite{delfly:design}. In contrast, there is little previous work 
on guidance of flapping wing MAVs. Baek demonstrated altitude control with an external 
camera~\cite{baek:altitude}. de Croon et al. demonstrated obstacle avoidance 
with an onboard camera and offboard processing~\cite{delfly:avoid}. For sub-20 gram
ornithopters, Baek et al. \cite{baek:tracking} is one of the few examples of
completely autonomous target seeking.
%[However, these papers do not study the system blah blah blah.]

@@

Rather than power-intensive PC processors, we used the ARM-based 
BeagleBoard single-board computer as reference computation platform. The
BeagleBoard consumes approximately 1 watt while running our computer vision 
and control algorithms. It uses the same processor as popular sub-10 gram 
processor modules---such as the Gumstix Overo and LogicPD Torpedo---which are 
light enough for deployment on millirobotic ground vehicles. We pair the 
BeagleBoard with an off-the-shelf consumer USB web camera, for similar image 
quality and resolution to the miniature camera modules available at 
millirobot scale. The BeagleBoard communicates with the H$^2$Bird using a 
USB radio module which implements the IEEE 802.15.4 wireless standard.
%TODO footnotes: Gumstix, LogidPD

@@

Attitude estimation and control for the H$^2$Bird runs on-board to achieve 
maintain high sample rate attitude control. We estimate the vehicle pose by naively
integrating the IMU, and use a proportional plus integral plus derivative (PID) 
controller for controlling the vehicle.

@@

The results of our experimental trials are shown in
Figs.~\ref{fig:flight_paths} and~\ref{fig:flight_paths_feasible}. For
initial conditions in the middle of the testing space and in front of the
camera, we achieved a success rate of 80\%. This case is depicted in
Fig.~\ref{fig:flight_paths_feasible}. As we moved towards the edges of the
feasible region in Fig.~\ref{fig:flight_paths}, the success rate diminishes
to 50\% because of several factors. On the edges of the camera frame, the yaw
control inputs are large in magnitude, although this is not necessary in all
cases. Since the control algorithm we are using has no notion of depth, it
applies the same control input whether the ornithopter is close to the camera,
where small changes in heading are adequate, or far away from the camera,
where large changes in heading are necessary. Due to this phenomenon, the
controller often over or under-compensates in certain regions, depending upon
the PID tuning and the distance from the camera. Tracking noise can also cause
passage negotiation to fail. Variations in the H$^2$Bird hand launch can cause
the system to respond differently for similar initial conditions. In addition,
the H$^2$Bird battery was changed approximately every 5 tests, adding more
variation to the H$^2$Bird performance by affecting the motor power output.
